Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-11 paper.tex
Clarify reasonnable expectations
Reviewer A:
  l'introduction me promet qu'elle va éclairer le design des
  algorithmes de cryptographie grâce à l'algèbre, et, finalement, je
  ne me sens que moyennement éclairé de ce point de vu.
  Principalement, l'article me dit qu'en abstrayant au maximum par
  rapport à une algèbre de Boole arbitraire, alors ça simplifie le
  raisonnement sur les algorithmes cryptographiques. Et c'est démontré
  de manière très convaincante. Mais ça ne me donne pas vraiment une
  nouvelle compréhension des algorithmes.

Reviewer C:
  Serait-il possible d'énoncer / prouver

>>>>

Note that the ambitions of our work stops at the level of
\emph{symmetric} cryptographic \emph{primitives} and, in particular,
their operational specification. These primitives would typically be
used (as black-boxes) in cryptographic \emph{protocols}: the analysis
of such protocols is out of the scope of the present work. Moreover,
we do not pretend that our conceptual apparatus could be useful to the
mathematical analysis of these primitives, as performed in a typical
``Section 2'', since this involves sophisticated, much more high-level
mathematical objects and results. Our focus is solely on shortening
the gap between an operational description of a primitive and its
efficient implementation. In effect, we are designing a programming
language dedicated to the description of symmetric cryptographic
primitives.
